formula1

### 2020-04-01 inst/formula1.Rmd
use pwa()

```{r,hamwetdrytest,cache=TRUE}
options(width = 80)
samep.test(L2017,c("Ham_wet","Ham_dry"))
```

>>>>

```{r,hamwetdrytest,cache=TRUE}
options(width = 80)
samep.test(L2017,c("Ham_wet","Ham_dry"))
```
(the p-value seems to be too low to be believable).

## Try the same thing but with function pwa()

```{r,trypwa,cache=TRUE}
f2017 <- read.table("formula1_2017.txt",header=TRUE)
f2017 <- f2017[,-ncol(f2017)]
details <- read.table("formula1_conditions.txt",header=TRUE)

H <- hyper2(pnames=c(rownames(f2017),"S"))
noscore <- c("Ret", "WD", "DNS", "DSQ", "DNP", "NC")

for(i in seq_len(ncol(f2017))){
	y <- f2017[,i]
	if(any(y %in% noscore)){y[y%in%noscore] <- 0}
	y <- as.numeric(levels(y)[y])
	names(y) <- rownames(f2017)
	cond <- details$conditions[i]
        jj <- ordervec2supp(y)
	if(cond == "dry"){
            pnames(jj) <- pnames(H)  # do nothing!
	} else if (cond == "wet"){
            jj <- pwa(jj,"Hamilton")
	} else {
            stop("neither wet nor dry?")
	}  # if wet closes
        H <- H + jj
} # i loop closes
head(H)
maxp(H)
#specificp.test(H,"S",0)
```

see this
